---
title: "Richness by combined zones"
abstract: |
  This is the abstract.
output: 
  html_document:
    code_folding: hide
    toc: true
date: "`r format(Sys.time(), '%d %B %Y')`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.align = 'center',
                      fig.height=8, 
                      fig.width=7, 
                      message=FALSE, 
                      warning=FALSE, 
                      cache=TRUE)

```

This notebook uses species richness layers created by SDM and polygons for three landscape variables to compare species richness distributions within the zones created by the three variables.  

The landscape variables/polygons are natural protected areas (ANPs), the 7 ecoregiones (aka. biomes) of Mexico, and landcover classified into vegetation, agriculture, and other. The ANP variable considers inside protected areas, within 10 km of the areas, and greater than 10 km from a protected area. These zone polygons were previously created (prep_create_zone_polygons.R).

The richness layers were created by stacking species distribution models (SDMs) that were produced for every species considered (process_SDM_v2.R). 

The result of the notebook is a collection of graphics displaying richness for each zone and indicating whether the differences in richness are statistically significant.

```{r initialize, message=FALSE}
# Load libraries and initialize variables
library(tidyverse)
library(patchwork)
library(rcompanion)
# sessionInfo()

# # Parameters (when running without knitting)
# To knit from console and programmatically specify parameters: rmarkdown::render(here::here('R', 'notebooks', 'richness_combined_zones', 'richness_by_combined_zones.Rmd'), params=params, output_file='richness_study.html')
if(!exists('params')){
  params <- list(
    unq_cells = TRUE,
    mutually_exclusive_pa = TRUE,
    filt_dates = FALSE,
    nspecies = 15,
    buffer_distance = 10,
    rich_code = 'Likhd',
    samp_n = 350, 
    rf_code = 'rf1')
}

# Filepath codes based on parameters
unq_code <- ifelse(params$mutually_exclusive_pa, 'unq_cells_exclusive', unq_code)
dfilt_code <- ifelse(params$filt_dates, '2000to2020', 'alldates')

# Directory paths
dat_dir <- here::here('data', 'data_out')

# Directory of richness tifs (predicted)
pred_dir <- file.path(dat_dir, 'sdm', str_c(unq_code, '_', dfilt_code), params$rf_code)

# Zones raster and lookup table
zones_fn <- 'stack_anps3_biomes7_usv3'
zone_polys_dir <- file.path(dat_dir, 'zone_polys')
zones_ras_fp <- file.path(zone_polys_dir, str_c(zones_fn, '.tif'))
zones_lu_fp <- file.path(zone_polys_dir, str_c(zones_fn, '_lu.rds'))

# Directory for richness dataframes
div_dir <- file.path(dat_dir, 'diversity_by_zones', 'from_richness', zones_fn)
dir.create(div_dir, recursive=TRUE, showWarnings = F)
```

Parameters:

* rich_code: **"`r params$rich_code`"**
* unq_cells: **`r params$unq_cells`**
* mutually_exclusive_pa: **`r params$mutually_exclusive_pa`**
* filt_dates: **`r params$filt_dates`**
* nspecies: **`r params$nspecies`**
* buffer_distance: **`r params$buffer_distance` km**
* samp_n: **`r params$samp_n`**

### Pre-process ANP, biome, and land use zones

```{r pre-process, eval=TRUE}
if(!file.exists(zones_ras_fp)){
  
  # File paths
  anps_fp <- file.path(zone_polys_dir, 'ANPs_buff10km.gpkg')
  biom_diss_fp <- file.path(zone_polys_dir, 'ecoregions_diss7.gpkg')
  usv_fn <- 'usv250s6gw_diss_3class.gpkg'
  usv_fp <- file.path(zone_polys_dir, usv_fn)

  # Input pollinator richness 
  pol_group <- 'Abejas'
  fp_tail <- file.path('sdm', str_c(unq_code, '_', dfilt_code), rf_code, pol_group)
  pred_dir <- here::here('data', 'data_out', fp_tail)
  rich_fn <- str_glue('{params$rich_code}_rich_{pol_group}_{dfilt_code}_{params$nspecies}species')
  rich_tif_fp <- here::here(pred_dir, str_glue('{rich_fn}.tif'))
  rich_ras <- terra::rast(rich_tif_fp)
    
  # ANP polys
  anps_ras_fp <- str_c(tools::file_path_sans_ext(anps_fp), '.tif')
  if(!file.exists(anps_ras_fp)){
    # ANP polys
    anps_polys <- terra::vect(anps_fp) 
    anps_diss <- terra::aggregate(anps_polys, by='zone')
    
    # Get lookup table
    anp_lu <- terra::values(anps_diss) %>% rownames_to_column('id') %>% 
      select(id, name=zone)
    anp_lu <- setNames(anp_lu$name, anp_lu$id)
    
    anp_lu
    
    # Rasterize and save
    anps_ras <- terra::rasterize(anps_diss, rich_ras)
    anps_ras %>% terra::writeRaster(anps_ras_fp, overwrite=T, 
                                    options=c("dstnodata=-99999"),
                                    wopt=list(gdal='COMPRESS=LZW'))
  } else {
    anps_ras <- terra::rast(anps_ras_fp)
  }
  
  # Biome polys
  biom_ras_fp <- str_c(tools::file_path_sans_ext(biom_diss_fp), '.tif')
  if(!file.exists(biom_ras_fp)){
    # Load polygons and dissolve
    biom_polys <- terra::vect(biom_diss_fp) 
    biom_diss <- terra::aggregate(biom_polys, by='DESECON1')
    
    # Get lookup table
    biom_lu <- terra::values(biom_diss) %>% rownames_to_column('id') %>% 
      select(id, name=DESECON1)
    biom_lu <- setNames(biom_lu$name, biom_lu$id)
  
    # Rasterize and save
    biom_ras <- terra::rasterize(biom_diss, rich_ras)
    biom_ras %>% terra::writeRaster(biom_ras_fp, overwrite=T, 
                                    options=c("dstnodata=-99999"),
                                    wopt=list(gdal='COMPRESS=LZW'))
  } else {
    biom_ras <- terra::rast(biom_ras_fp)
  }
  
  # Land use polys
  usv_ras_fp <- str_c(tools::file_path_sans_ext(usv_fp), '.tif')
  if(!file.exists(usv_ras_fp)){
    # Load polygons
    usv_polys <- terra::vect(usv_fp)

    # Get lookup table
    usv_lu <- terra::values(usv_polys) %>% 
      rownames_to_column('id') %>% 
      select(id, name=tipo)
    usv_lu <- setNames(usv_lu$name, usv_lu$id)
  
    # Rasterize and save
    usv_ras <- terra::rasterize(usv_polys, rich_ras)
    usv_ras %>% terra::writeRaster(usv_ras_fp, 
                                 overwrite=T, options=c("dstnodata=-99999"), 
                                 wopt=list(gdal='COMPRESS=LZW'))
  } else {
    usv_ras <- terra::rast(usv_ras_fp)
  }
  
  # Combine zone rasters
  combo_ras <- c(anps_ras, biom_ras, usv_ras)
  names(combo_ras) <- c('anp_zone', 'biome', 'usv')
  
  combo_ras %>% terra::writeRaster(zones_ras_fp, 
                                 overwrite=T, options=c("dstnodata=-99999"), 
                                 wopt=list(gdal='COMPRESS=LZW'))
  
  saveRDS(list(anp=anp_lu, biom=biom_lu, usv=usv_lu), file=zones_lu_fp)
} 
```

### Richness data frames

Convert rasters to dataframes of richness by ANP zone, biome, land cover, and pollinator group. 

```{r make div_df}
# Load stacked zones
combo_ras <- terra::rast(zones_ras_fp)
lu <- readRDS(zones_lu_fp)

# List richness tifs
tif_query <- str_glue(
  '{params$rich_code}_rich_.*_{dfilt_code}_{params$nspecies}species.tif')
fps <- list.files(pred_dir, pattern=tif_query, recursive=T, full.names=T)

for(rich_tif_fp in fps){
  
  # Resulting path for CSV
  rich_fn <- basename(tools::file_path_sans_ext(rich_tif_fp))
  pol_group <- str_extract(rich_fn, 'Abejas|Mariposas|Colibries|Murcielagos|Avispas|Moscas')
  div_df_fp <- file.path(div_dir, str_c(rich_fn, '.csv'))
  
  if(!file.exists(div_df_fp)){
    
    # Load raster and add to SpatRaster
    rich_ras <- terra::rast(rich_tif_fp)
    names(rich_ras) <- 'richness'
    combo_all <- c(combo_ras, rich_ras)
    
    # Convert to DF and recode
    div_df <- terra::as.data.frame(combo_all, cells=TRUE) %>% 
      mutate(pol_group = pol_group)
    
    # Save
    div_df %>% write_csv(div_df_fp)
    
  }
}
```

Combine pollinator richness dataframes into one dataframe with all pollinators.

```{r}
# Load DFs and row bind
fps <- list.files(div_dir, pattern='csv$', full.name=T) %>% 
    str_subset(str_glue('/{params$rich_code}.*{dfilt_code}'))
div_df1 <- fps %>% purrr::map_dfr(read_csv, col_types='ifffdf')

# Recode biome names
biom_codes_all <- tibble(id=names(lu$biom), 
                     name=lu$biom, 
       code=c('CalMedit', 'Desierto', 'ElevSemiar', 'GranPlanic', 
              'SelvCalHum', 'SelvCalSec', 'SierTemp'))
biom_codes <- setNames(biom_codes_all$code, biom_codes_all$id)

# Convert numeric code to factors
div_df <- div_df1 %>% 
      mutate(anp_zone = recode(anp_zone, !!!lu$anp) %>% 
               factor(levels = c('Outside buffer', 'Buffer 10 km', 'Inside NPA')),
             biome = recode(biome, !!!biom_codes) %>% 
               factor(),
             usv = recode(usv, !!!lu$usv) %>% 
               factor(levels = c('veg', 'ag', 'otro')))

```

### Compare richness by zones - ANP zones

The function `get_grp_diffs` evaluates the statistical significance of groups and returns medians, CIs, and significant groups for plotting. It will be applied to each group of pollinator, biome, and either ANP zone or land cover type.

```{r get_grp_diffs}
get_grp_diffs <- function(df, grp_var){
  
  # Get medians and confidence intervals
  f <- str_c('richness ~ ', grp_var)
  Sum <- do.call("groupwiseMedian", 
          list(as.formula(f), 
               data = as.name('df'),
               conf       = 0.95,
                R          = 5000,
                percentile = TRUE,
                bca        = FALSE,
                digits     = 3))
  
  if(length(unique(df[[grp_var]])) == 1) {
    
    print('Only one group.')
    cld <- tibble(zone = unique(df[[grp_var]]), sig_group = 'a')
    
  } else {
    
    # Check whether any groups are significantly different
    kw <- kruskal.test(df[['richness']] ~ df[[grp_var]]) 
    if(kw$p.value > 0.05) print('No significantly different groups')
    
    # Post-hoc test to compare groups
    PT <- pairwise.wilcox.test(df[['richness']], df[[grp_var]], 
                               p.adjust.method = 'fdr')
    PT1 = rcompanion::fullPTable(PT$p.value)
    cld_list <- multcompView::multcompLetters(PT1,
                  compare="<",
                  threshold=0.05,  # p-value to use as significance threshold
                  Letters=letters,
                  reversed = FALSE)
    lv <- cld_list$Letters
    cld <- tibble(sig_group = factor(lv, levels = sort(unique(lv))), 
                  zone = factor(names(lv)))
  
  }

  # Join letter indicating significantly different groups to medians and CIs
  sum1 <- select(tibble(cld), zone, sig_group) %>% 
    left_join(tibble(Sum), 
              by=c(zone=grp_var))
  
  return(sum1)
}
```

```{r plot_pollin_facet, echo=F}
plot_pollin_facet <- function(df, pol_grp, var2='usv', grp_var='anp_zone', 
                              patch.position='inner', legend_on=FALSE){
  
  xmax <- max(df$Percentile.upper)
  
  df_rect <- distinct(df, biome, .data[[var2]], pol_group)
  if(grp_var == 'anp_zone'){
    
    var_levels <- c( 'Outside buffer', 'Buffer 10 km', 'Inside NPA')
    facet_y <- 'Land cover'
    
  } else if (grp_var == 'usv') {
    
    var_levels <- c( 'otro', 'ag', 'veg')
    facet_y <- 'ANP zone'
    
  }
  
  if(var2 != 'pol_group'){
     p <- ggplot(df) +
       
      # shade facet by ANP zone
      geom_rect(data=df_rect, aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf,
                    fill=.data[[var2]]), alpha=0.25, color='white') +
      scale_fill_grey(name = facet_y, start=0.05, end=0.75) 
     
  } else {
    
    p <- ggplot(df)
    
  }
  
  p <- p +
  
    # plot CIs
    geom_errorbar(aes(y = zone, x = Median, color=sig_group,
                      xmin = Percentile.lower, xmax = Percentile.upper),
                   width = 0.3, size  = 0.5) +
    
    # plot medians
     geom_point(aes(y = zone, x = Median, color=sig_group), 
                shape = 15, size  = 2) +
     xlab("Median richness with 95% CI") +
    
    scale_color_manual(values=c('a'='#F8766D', 'ab'='#C77CFF', 'b'='#00BFC4', 
                       'bc'='#7CAE00', 'c'='#DE8C00'), 
                       # limits = c('a', 'ab', 'b', 'bc', 'c'),
                       name='Group',
                       drop=FALSE) +
      
    scale_y_discrete(limits = var_levels) +
    scale_x_continuous(n.breaks= 3) +
  
    # Facet by x=pollinator group, y = ANP zone
    facet_grid(vars(.data[[var2]]), vars(biome)) +
    ggtitle(pol_grp) +
    theme_minimal() +
    theme(
      plot.title = element_text(size=rel(1), face='bold', hjust=0),
      panel.spacing = unit(0.5, 'mm'),
      panel.border=element_blank(),
      # panel.grid = element_line(color='darkgray'), 
      # panel.grid.minor.x = element_line(color='darkgray'),
      panel.grid.major.y=element_blank(),
      panel.ontop = FALSE,
      panel.background = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(), 
      axis.ticks.y = element_blank(),
      # axis.text.x = element_text(margin = margin(t = .2, unit = "mm")),
      strip.text = element_blank(),
      strip.background = element_blank(),
      strip.switch.pad.grid = unit(0.5, 'mm'),
      legend.position = 'none'
      )
  
  return(p)
  
}
```

#### Sample DF

Create stratified random sample of pollinator richness values. `r params$samp_n` pixels are sampled from each unique combination biome, land cover type, and ANP zone. The same pixels are sample for each pollinator group, i.e. each pollinator richness layer.

```{r sample-df}
# Stratified random sample
fn <- str_c('samp', params$samp_n, '_', params$rich_code, '_', 
            dfilt_code, '_', params$nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
samp_fp <- file.path(div_dir, fn)

if(!file.exists(samp_fp)){
  # Sample the same cells for all the pollinator groups
  
  # Get all usable cells
  samp_idx <- div_df %>% 
    filter(pol_group == 'Abejas') %>% 
    group_by(anp_zone, biome, usv) %>%
    filter(n() > params$samp_n)
  
  # Random sample stratified by group
  set.seed(1)
  samp_idx <- samp_idx %>% 
    do(slice_sample(., n=params$samp_n)) %>%
    ungroup
  
  df_samp <- div_df %>% filter(cell %in% samp_idx$cell)
  
  # Save
  df_samp %>% saveRDS(samp_fp)
  
} else {
  
  df_samp <- readRDS(samp_fp)
  
}
```

### Compare groups
#### Compare by land cover type

```{r compare-usv-x-anp}
grp_var <- 'usv'
var2 <- 'anp_zone'

# File name
fn <- str_c('grpdiffs_samp', params$samp_n, '_', 
            grp_var, '_', 
            params$rich_code, '_', 
            dfilt_code, '_', 
            params$nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  sum2 <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  sg_levels <- sort(as.character(unique(sum2$sig_group)))
  sum2 <- sum2 %>% mutate(sig_group = factor(sig_group, 
                                              levels = sg_levels))
  
  # Save 
  sum2 %>% saveRDS(grp_diffs_fp)
  
} else {
  
  sum2 <- readRDS(grp_diffs_fp)
  
}
```

```{r plot-usv-x-anp, fig.width=7, fig.height=8, cache=T}
pol_groups <- levels(sum2$pol_group)

# Plot
p1 <- sum2 %>% filter(pol_group == pol_groups[1]) %>% 
  plot_pollin_facet(pol_groups[1], var2=var2, grp_var=grp_var) +
  theme(strip.text.x = element_text(size=rel(0.8)),
        plot.title = element_text(vjust=0),
        axis.title.x = element_blank())
p2 <- sum2 %>% filter(pol_group == pol_groups[2]) %>% 
  plot_pollin_facet(pol_groups[2], var2=var2, grp_var=grp_var) +
  theme(legend.position = 'right',
        axis.title.x = element_blank())
p3 <- sum2 %>% filter(pol_group == pol_groups[3]) %>% 
  plot_pollin_facet(pol_groups[3], var2=var2, grp_var=grp_var) +
  theme(axis.title.x = element_blank())

# Vary the plotting based on whether we're looking at 3 or 4 groups
if(length(pol_groups) == 3){
  p3 <- p3 + theme(
    axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ),
    axis.title.x = element_text())
  
  plots <- list(p1, p2, p3)
  
} else if(length(pol_groups) == 4) {
  
  p4 <- sum2 %>% filter(pol_group == pol_groups[4]) %>% 
    plot_pollin_facet(pol_groups[4], var2=var2, grp_var=grp_var) +
    theme(axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1)
                                   # using a vector here may be deprecated. 
                                   # Alternatives: ggtext + element_markdown()? 
                                   ),
          axis.title.x = element_text())

  plots <- list(p1, p2, p3, p4)
}

# Put the plots together
wrap_plots(plots, ncol=1, guides = 'collect') +
  plot_annotation(
    caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.") & 
  scale_x_continuous(n.breaks=3,
                     limits = c(0, 10)) &
  theme(plot.title.position = 'plot')

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', params$samp_n, '_', 
                          grp_var, '_', 
                          params$rich_code, '_', 
                          dfilt_code, '_',
                          params$nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, height=8)
```

#### Compare by ANP zone

```{r compare-anp-x-usv}
grp_var <- 'anp_zone'
var2 <- 'usv'

# File name
fn <- str_c('grpdiffs_samp', params$samp_n, '_', grp_var, '_', params$rich_code, '_', 
            dfilt_code, '_', params$nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  sum2 <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  sg_levels <- sort(as.character(unique(sum2$sig_group)))
  sum2 <- sum2 %>%
    mutate(sig_group = factor(sig_group, levels = sg_levels))
  
  # Save 
  sum2 %>% saveRDS(grp_diffs_fp)
  
} else {
  
  sum2 <- readRDS(grp_diffs_fp)
  
}
```

```{r plot-anp-x-usv, fig.height=8, fig.width=7, cache=TRUE}
pol_groups <- levels(sum2$pol_group)

# Plot
p1 <- sum2 %>% filter(pol_group == pol_groups[1]) %>% 
  plot_pollin_facet(pol_groups[1], var2=var2, grp_var=grp_var) +
  theme(strip.text.x = element_text(size=rel(0.8)),
        plot.title = element_text(vjust=0),
        axis.text.x = element_blank())
p2 <- sum2 %>% filter(pol_group == pol_groups[2]) %>% 
  plot_pollin_facet(pol_groups[2], var2=var2, grp_var=grp_var) +
  theme(legend.position = 'right',
        axis.text.x = element_blank())
p3 <- sum2 %>% filter(pol_group == pol_groups[3]) %>% 
  plot_pollin_facet(pol_groups[3], var2=var2, grp_var=grp_var) +
  theme(axis.text.x = element_blank())

# Vary the plotting based on whether we're looking at 3 or 4 groups
if(length(pol_groups) == 3){
  p3 <- p3 + theme(
    axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ))
  
  plots <- list(p1, p2, p3)
  
} else if(length(pol_groups) == 4) {
  
  p4 <- sum2 %>% filter(pol_group == pol_groups[4]) %>% 
    plot_pollin_facet(pol_groups[4], var2=var2, grp_var=grp_var) +
    theme(axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ))

  plots <- list(p1, p2, p3, p4)
}

# Put the plots together
wrap_plots(plots, ncol=1, 
           guides = 'collect') +
  plot_annotation(
    caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.") & 
  scale_x_continuous(n.breaks=3,
                     limits = c(0, 10)) &
  theme(plot.title.position = 'plot')

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', params$samp_n, '_', 
                          grp_var, '_',  params$rich_code, '_',
                          dfilt_code, '_', params$nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, height=8)
```

#### Compare by ANP zone without land cover

```{r compare-anp, fig.width=7, fig.height=4, cache=T}
grp_var <- 'anp_zone'
var2 <- NA

# File name
fn <- str_c('grpdiffs_samp', params$samp_n, '_', 
            grp_var, '_', 'noUSV_',
            params$rich_code, '_', 
            dfilt_code, '_', params$nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  if(is.na(var2)){
    df_nest <- df_samp %>% group_by(pol_group, biome) %>% nest()
  } else {
    df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  }
  medians_anp <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  sg_levels <- sort(as.character(unique(medians_anp$sig_group)))
  medians_anp <- medians_anp %>% mutate(sig_group = factor(sig_group, 
                                              levels = sg_levels))
  
  # Save 
  medians_anp %>% saveRDS(grp_diffs_fp)
  
} else {
  
  medians_anp <- readRDS(grp_diffs_fp)
  
}

# Plot
medians_anp %>% 
  plot_pollin_facet('All', var2='pol_group', grp_var=grp_var) +
    scale_x_continuous(n.breaks= 4) +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin= margin(t=6, unit='pt')),
        axis.text.x = element_text(hjust=c(0, 0.5, 1)), 
        plot.title = element_blank(), 
        legend.position = 'bottom', 
        legend.box.spacing = unit(1, 'pt'),
        strip.text = element_text(size=rel(0.8)),
        panel.background = element_rect(fill=alpha('#A6A6A6', 0.3), 
                                        color='white'),
        panel.grid = element_line(color='lightgray'),
        panel.grid.minor.x = element_line(color='lightgray')
        ) +
    labs(caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.")

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', params$samp_n, '_', 
                          grp_var, '_', 'noUSV_',
                          params$rich_code, '_', 
                          dfilt_code, '_', 
                          params$nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, width=9, height=4)
```

#### Compare by land cover without ANP zone

```{r compare-usv, fig.height=4, fig.width=7, warning=FALSE, cache=TRUE}
grp_var <- 'usv'
var2 <- NA

# File name
fn <- str_c('grpdiffs_samp', params$samp_n, '_', 
            grp_var, '_', 'noANP_',
            params$rich_code, '_', 
            dfilt_code, '_', params$nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  if(is.na(var2)){
    df_nest <- df_samp %>% group_by(pol_group, biome) %>% nest()
  } else {
    df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  }
  
  # compare richness distribution within groups
  medians_usv <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  # establish order for letters (significant groups)
  sg_levels <- sort(as.character(unique(medians_usv$sig_group)))
  medians_usv <- medians_usv %>% mutate(sig_group = factor(sig_group, 
                                              levels = sg_levels))
  
  # Save 
  medians_usv %>% saveRDS(grp_diffs_fp)
  
} else {
  
  medians_usv <- readRDS(grp_diffs_fp)
  
}

# Plot
medians_usv %>% 
  plot_pollin_facet('All', var2='pol_group', grp_var=grp_var) +
    scale_x_continuous(n.breaks= 4) +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin= margin(t=6, unit='pt')),
        axis.text.x = element_text(hjust=c(0, 0.5, 1)), 
        plot.title = element_blank(), 
        legend.position = 'bottom', 
        legend.box.spacing = unit(1, 'pt'),
        strip.text = element_text(size=rel(0.8)),
        panel.background = element_rect(fill=alpha('#A6A6A6', 0.3), 
                                        color='white'),
        panel.grid = element_line(color='lightgray'),
        panel.grid.minor.x = element_line(color='lightgray')
        ) +
    labs(caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.")

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', params$samp_n, '_', 
                          grp_var, '_', 'noANP_',
                          params$rich_code, '_', 
                          dfilt_code, '_', 
                          params$nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, width=9, height=4)
```











#### Exploratory Plots

```{r, eval=FALSE}
# Plot all groups with facets by biome and pollinators
div_df %>%
  filter(pol_group == 'Colibries', biome== 'Selvas Calido-Secas') %>%
  ggplot(., aes(y=richness, color=usv, fill=usv, x=anp_zone)) +
  geom_boxplot(outlier.size=1, 
                 outlier.alpha = 0.5,
                 # fill=NA, 
               alpha=0.5,
                 width = .85, 
                 notch=T,
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill'), 
                        "Uso de suelo") +
  theme(legend.position = 'bottom') +
  labs(x=NULL, y='Richness') +
  facet_grid(vars(pol_group), vars(biome))

# Plot richness by ANP zone, faceted by biome
div_df %>%
  ggplot(., aes(y=richness, color=anp_zone, fill=anp_zone, x=anp_zone)) +
  geom_boxplot(outlier.size=1, outlier.alpha = 0.5,
               alpha=0.5,
                 notch=T,
                 width = .85, 
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill')) +
  theme(legend.position = 'none') +
  labs(x=NULL) +
  facet_wrap(facets=vars(biome))
```

#### Check for significant differences in groups

```{r compare abejas, eval=FALSE}
abejas_df <- div_df %>% filter(pol_group == 'Abejas')
m <- lm(richness ~ anp_zone, data = abejas_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(anp_zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
# 
# abejas_df %>% 
#   ggplot(., aes(x=richness, fill=zone, y=zone)) +
#   geom_boxplot() +
#   theme(legend.position = 'none')  +
#   labs(y=NULL) 

# Kruskal-Wallis test
kruskal.test(richness ~ anp_zone, data = abejas_df) 
kruskal.test(richness ~ biome, data = abejas_df) 
kruskal.test(richness ~ usv, data = abejas_df) 

# Stratified random sample
df_samp <- abejas_df %>%
  filter(biome=='Selvas Calido-Secas', usv=='veg') %>% 
  group_by(anp_zone) %>% 
  do(sample_n(., 20000))
df_samp <- abejas_df %>%
  group_by(anp_zone, biome, usv) %>% 
  do(sample_n(., 64))
kruskal.test(richness ~ anp_zone, data = df_samp) 

# Effect size stats
# 
rcompanion::epsilonSquared(x=df_samp$richness, g=df_samp$anp_zone)
# Freeman's theta == 1 means all values in group are greater (or less) than all values in other group. 0 means groups are stochastically equal. 
rcompanion::freemanTheta(x=df_samp$richness, g=df_samp$anp_zone)
# Vargha and Delaney's A (VDA): probability that an observation from one group is greater than an observation from the other group. Use maximum for overall.
rcompanion::multiVDA(x=df_samp$richness, g=df_samp$anp_zone)

# Post-hoc test
# Dunn test
(DT = FSA::dunnTest(richness ~ anp_zone, data = df_samp, method='bh'))
PT = DT$res
cld <- rcompanion::cldList(P.adj ~ Comparison,
        data = PT,
        threshold = 0.05)

# Plot medians and confidence intervals
Sum = rcompanion::groupwiseMedian(richness ~ anp_zone,
                      data       = df_samp,
                      conf       = 0.95,
                      R          = 5000,
                      percentile = TRUE,
                      bca        = FALSE,
                      digits     = 3)
sum1 <- tibble(Sum) %>% 
  mutate(temp_zone = str_remove_all(anp_zone, ' |0')) %>% 
  left_join(select(tibble(cld), zone, sig_group), by=c(temp_zone='zone'))

ggplot(sum1, aes(x = anp_zone, y = Median, color=sig_group)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 4) +
   ylab("Median richness with 95% CI")
```
