---
title: "Richness by combined zones"
output: html_document
date: 2021-03-23
editor_options: 
  chunk_output_type: console
params:
  unq_cells: TRUE
  mutually_exclusive_pa: TRUE
  filt_dates: TRUE
  nspecies: 15
  buffer_distance: 10
  rich_code: 'Likhd'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Load libraries and initialize variables

#### Parameters

rich_code: `params$rich_code`
unq_cells: `params$unq_cells`
mutually_exclusive_pa: `params$mutually_exclusive_pa`
filt_dates: `params$filt_dates`
nspecies: `params$nspecies`
buffer_distance: `params$buffer_distance` km

```{r initialize, message=FALSE}
library(tidyverse)
library(patchwork)
# sessionInfo()

# Parameters (when running without knitting)
params <- list(
  unq_cells = TRUE,
  mutually_exclusive_pa = TRUE,
  filt_dates = FALSE,
  nspecies = 15,
  buffer_distance = 10,
  rich_code = 'Likhd')

# Directory paths
zones_fn <- 'stack_anps3_biomes7_usv3'
zone_polys_dir <- here::here('data', 'data_out', 'zone_polys')
zones_ras_fp <- file.path(zone_polys_dir, str_c(zones_fn, '.tif'))
zones_lu_fp <- file.path(zone_polys_dir, str_c(zones_fn, '_lu.rds'))

# Directory paths
unq_code <- ifelse(params$mutually_exclusive_pa, 'unq_cells_exclusive', unq_code)
datefilt_code <- ifelse(params$filt_dates, '2000to2020', 'alldates')
```

## Pre-process ANP, biome, and land use zones

```{r pre-process, eval=TRUE}
if(!file.exists(zones_ras_fp)){
  
  # File paths
  anps_fp <- file.path(zone_polys_dir, 'ANPs_buff10km.gpkg')
  biom_diss_fp <- file.path(zone_polys_dir, 'ecoregions_diss7.gpkg')
  usv_fn <- 'usv250s6gw_diss_3class.gpkg'
  usv_fp <- file.path(zone_polys_dir, usv_fn)

   
  # Input pollinator richness 
  pol_group <- 'Abejas'
  fp_tail <- file.path('sdm', str_c(unq_code, '_', datefilt_code), 'rf1', pol_group)
  pred_dir <- here::here('data', 'data_out', fp_tail)
  rich_fn <- str_glue('{params$rich_code}_rich_{pol_group}_{datefilt_code}_{params$nspecies}species')
  rich_tif_fp <- here::here(pred_dir, str_glue('{rich_fn}.tif'))
  rich_ras <- terra::rast(rich_tif_fp)
    
  # ANP polys
  anps_ras_fp <- str_c(tools::file_path_sans_ext(anps_fp), '.tif')
  if(!file.exists(anps_ras_fp)){
    # ANP polys
    anps_polys <- terra::vect(anps_fp) 
    anps_diss <- terra::aggregate(anps_polys, by='zone')
    
    # Get lookup table
    anp_lu <- terra::values(anps_diss) %>% rownames_to_column('id') %>% 
      select(id, name=zone)
    anp_lu <- setNames(anp_lu$name, anp_lu$id)
    
    anp_lu
    
    # Rasterize and save
    anps_ras <- terra::rasterize(anps_diss, rich_ras)
    anps_ras %>% terra::writeRaster(anps_ras_fp, overwrite=T, 
                                    options=c("dstnodata=-99999"),
                                    wopt=list(gdal='COMPRESS=LZW'))
  } else {
    anps_ras <- terra::rast(anps_ras_fp)
  }
  
  # Biome polys
  biom_ras_fp <- str_c(tools::file_path_sans_ext(biom_diss_fp), '.tif')
  if(!file.exists(biom_ras_fp)){
    # Load polygons and dissolve
    biom_polys <- terra::vect(biom_diss_fp) 
    biom_diss <- terra::aggregate(biom_polys, by='DESECON1')
    
    # Get lookup table
    biom_lu <- terra::values(biom_diss) %>% rownames_to_column('id') %>% 
      select(id, name=DESECON1)
    biom_lu <- setNames(biom_lu$name, biom_lu$id)
  
    # Rasterize and save
    biom_ras <- terra::rasterize(biom_diss, rich_ras)
    biom_ras %>% terra::writeRaster(biom_ras_fp, overwrite=T, 
                                    options=c("dstnodata=-99999"),
                                    wopt=list(gdal='COMPRESS=LZW'))
  } else {
    biom_ras <- terra::rast(biom_ras_fp)
  }
  
  # Land use polys
  usv_ras_fp <- str_c(tools::file_path_sans_ext(usv_fp), '.tif')
  if(!file.exists(usv_ras_fp)){
    # Load polygons
    usv_polys <- terra::vect(usv_fp)

    # Get lookup table
    usv_lu <- terra::values(usv_polys) %>% 
      rownames_to_column('id') %>% 
      select(id, name=tipo)
    usv_lu <- setNames(usv_lu$name, usv_lu$id)
  
    # Rasterize and save
    usv_ras <- terra::rasterize(usv_polys, rich_ras)
    usv_ras %>% terra::writeRaster(usv_ras_fp, 
                                 overwrite=T, options=c("dstnodata=-99999"), 
                                 wopt=list(gdal='COMPRESS=LZW'))
  } else {
    usv_ras <- terra::rast(usv_ras_fp)
  }
  
  # Combine zone rasters
  combo_ras <- c(anps_ras, biom_ras, usv_ras)
  names(combo_ras) <- c('anp_zone', 'biome', 'usv')
  
  combo_ras %>% terra::writeRaster(zones_ras_fp, 
                                 overwrite=T, options=c("dstnodata=-99999"), 
                                 wopt=list(gdal='COMPRESS=LZW'))
  
  saveRDS(list(anp=anp_lu, biom=biom_lu, usv=usv_lu), file=zones_lu_fp)
} 
```

## Diversity data frames

Create dataframes with ANP zone, biome, land cover, and richness by pollinator group where each row is a pixel. 

```{r make div_df}
pol_group <- 'Mariposas'

# # Get cells for stratified random sample - INCOMPLETE
# combo_ras <- terra::rast(zones_ras_fp)
# sample <- terra::spatSample(combo_ras, size=64, cells=TRUE, strata=combo_ras) 
# unq <- combo_ras %>% terra::unique()               
# lu <- as_tibble(unq) %>% rownames_to_column() %>% 
#   mutate(rowname = as.numeric(rowname))
# 
# lu_row <- function(anp_zone, biome, usv, lu) {
#   lu_row <- right_join(lu, tibble(anp_zone, biome, usv))
#   val <- lu_row %>% transmute(rowname = as.numeric(rowname)) %>% deframe()
# }
# 
# x <- combo_ras %>% terra::lapp(fun=lu_row, lu=lu)
# terra::plot(x)           

# Output directory
div_dir <- here::here('data', 'data_out', 'diversity_by_zones', 
                      'from_richness', zones_fn)
dir.create(div_dir, recursive=TRUE, showWarnings = F)

# Load stacked zones
combo_ras <- terra::rast(zones_ras_fp)
lu <- readRDS(zones_lu_fp)
    
for(pol_group in c('Abejas', 'Colibries', 'Mariposas', 'Murcielagos')){

  fp_tail <- file.path('sdm', str_c(unq_code, '_', datefilt_code), 'rf1', pol_group)
  pred_dir <- here::here('data', 'data_out', fp_tail)

  # Input pollinator richness
  rich_fn <- str_glue('{params$rich_code}_rich_{pol_group}_{datefilt_code}_{params$nspecies}species')
  rich_tif_fp <- here::here(pred_dir, str_glue('{rich_fn}.tif'))
  
  # Resulting path for CSV
  div_df_fp <- file.path(div_dir, str_c(rich_fn, '.csv'))
  
  if(!file.exists(div_df_fp)){
    
    # Load raster and add to SpatRaster
    rich_ras <- terra::rast(rich_tif_fp)
    names(rich_ras) <- 'richness'
    combo_all <- c(combo_ras, rich_ras)
    
    # Convert to DF and recode
    div_df <- terra::as.data.frame(combo_all, cells=TRUE) %>% 
      mutate(pol_group = pol_group)
    
    # Save
    div_df %>% write_csv(div_df_fp)
    
    # div_df <- div_df %>% 
    #   mutate(anp_zone = recode(anp_zone, !!!lu$anp),
    #          biome = recode(biome, !!!lu$biom),
    #          usv = recode(usv, !!!lu$usv))
    # 
    # # Save
    # div_df %>% write_csv(div_df_fp)
    
  }
}

# Load DFs and row bind
(fps <- list.files(div_dir, pattern='csv$', full.name=T) %>% 
    str_subset(str_glue('/{params$rich_code}.*{datefilt_code}')))
div_df1 <- fps %>% purrr::map_dfr(read_csv, col_types='ifffdf')

# Recode biome names
biom_codes_all <- tibble(id=names(lu$biom), 
                     name=lu$biom, 
       code=c('CalMedit', 'Desierto', 'ElevSemiar', 'GranPlanic', 
              'SelvCalHum', 'SelvCalSec', 'SierTemp'))
biom_codes <- setNames(biom_codes_all$code, biom_codes_all$id)

# Convert numeric code to factors
div_df <- div_df1 %>% 
      mutate(anp_zone = recode(anp_zone, !!!lu$anp) %>% 
               factor(levels = c('Inside NPA', 'Buffer 10 km', 'Outside buffer')),
             biome = recode(biome, !!!biom_codes) %>% factor(),
             usv = recode(usv, !!!lu$usv) %>% 
               factor(levels = c('veg', 'ag', 'otro')))

```

=====
## Exploratory Plots

```{r}
# Plot all groups with facets by biome and pollinators
div_df %>%
  filter(pol_group == 'Colibries', biome== 'Selvas Calido-Secas') %>%
  ggplot(., aes(y=richness, color=usv, fill=usv, x=anp_zone)) +
  geom_boxplot(outlier.size=1, 
                 outlier.alpha = 0.5,
                 # fill=NA, 
               alpha=0.5,
                 width = .85, 
                 notch=T,
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill'), 
                        "Uso de suelo") +
  theme(legend.position = 'bottom') +
  labs(x=NULL, y='Richness') +
  facet_grid(vars(pol_group), vars(biome))

# Plot richness by ANP zone, faceted by biome
div_df %>%
  ggplot(., aes(y=richness, color=anp_zone, fill=anp_zone, x=anp_zone)) +
  geom_boxplot(outlier.size=1, outlier.alpha = 0.5,
               alpha=0.5,
                 notch=T,
                 width = .85, 
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill')) +
  theme(legend.position = 'none') +
  labs(x=NULL) +
  facet_wrap(facets=vars(biome))
```

## Check for significant differences in groups
### Abejas

```{r compare abejas, echo=TRUE}
abejas_df <- div_df %>% filter(pol_group == 'Abejas')
m <- lm(richness ~ anp_zone, data = abejas_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(anp_zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
# 
# abejas_df %>% 
#   ggplot(., aes(x=richness, fill=zone, y=zone)) +
#   geom_boxplot() +
#   theme(legend.position = 'none')  +
#   labs(y=NULL) 

# Kruskal-Wallis test
kruskal.test(richness ~ anp_zone, data = abejas_df) 
kruskal.test(richness ~ biome, data = abejas_df) 
kruskal.test(richness ~ usv, data = abejas_df) 

# Stratified random sample
df_samp <- abejas_df %>%
  filter(biome=='Selvas Calido-Secas', usv=='veg') %>% 
  group_by(anp_zone) %>% 
  do(sample_n(., 20000))
df_samp <- abejas_df %>%
  group_by(anp_zone, biome, usv) %>% 
  do(sample_n(., 64))
kruskal.test(richness ~ anp_zone, data = df_samp) 

# Effect size stats
# 
rcompanion::epsilonSquared(x=df_samp$richness, g=df_samp$anp_zone)
# Freeman's theta == 1 means all values in group are greater (or less) than all values in other group. 0 means groups are stochastically equal. 
rcompanion::freemanTheta(x=df_samp$richness, g=df_samp$anp_zone)
# Vargha and Delaney's A (VDA): probability that an observation from one group is greater than an observation from the other group. Use maximum for overall.
rcompanion::multiVDA(x=df_samp$richness, g=df_samp$anp_zone)

# Post-hoc test
# Dunn test
(DT = FSA::dunnTest(richness ~ anp_zone, data = df_samp, method='bh'))
PT = DT$res
cld <- rcompanion::cldList(P.adj ~ Comparison,
        data = PT,
        threshold = 0.05)

# Plot medians and confidence intervals
Sum = rcompanion::groupwiseMedian(richness ~ anp_zone,
                      data       = df_samp,
                      conf       = 0.95,
                      R          = 5000,
                      percentile = TRUE,
                      bca        = FALSE,
                      digits     = 3)
sum1 <- tibble(Sum) %>% 
  mutate(temp_zone = str_remove_all(anp_zone, ' |0')) %>% 
  left_join(select(tibble(cld), Group, Letter), by=c(temp_zone='Group'))

ggplot(sum1, aes(x = anp_zone, y = Median, color=Letter)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 4) +
   ylab("Median richness with 95% CI")
```

=====
### Define function 

The function `get_grp_differences` evaluates the statistical significance of groups and return medians,  CIs, and significant groups for plotting. It will be applied to each group of pollinator, biome, and ANP zone. 

```{r}
get_grp_differences_wilcox <- function(df){
  
  # Check whether any groups are significantly different
  kw <- kruskal.test(richness ~ usv, data = df) 
  if(kw$p.value > 0.05) print('No significantly different groups')
  
  # Post-hoc test to compare groups
  PT <- pairwise.wilcox.test(df$richness, df$usv, p.adjust.method = 'fdr')
  PT = PT$p.value
  PT1 = rcompanion::fullPTable(PT)
  cld_list <- multcompView::multcompLetters(PT1,
                compare="<",
                threshold=0.05,  # p-value to use as significance threshold
                Letters=letters,
                reversed = FALSE)
  cld <- tibble(Letter=cld_list$Letters, Group=names(cld_list$Letters))
  
  # Plot medians and confidence intervals
  Sum = rcompanion::groupwiseMedian(richness ~ usv,
                        data       = df,
                        conf       = 0.95,
                        R          = 5000,
                        percentile = TRUE,
                        bca        = FALSE,
                        digits     = 3)
  
  # Join letter indicating significantly different groups to medians and CIs
  sum1 <- tibble(Sum) %>% 
    mutate(temp_zone = str_remove_all(usv, ' |0')) %>% 
    left_join(select(tibble(cld), Group, Letter), by=c(temp_zone='Group')) %>% 
    select(-temp_zone)
  
  return(sum1)
}
```

### Sample div DF

```{r}
# Get DF
df_samp <- div_df %>%
  group_by(pol_group, anp_zone, biome, usv) %>%
  do(sample_n(., 64)) %>%
  ungroup

# Get DF
df_samp <- div_df %>%
  group_by(pol_group, anp_zone, biome, usv) %>%
  filter(n() > 100) %>% 
  ungroup() %>% 
  sample_n(50000)

df_samp <- div_df %>%
  group_by(pol_group, anp_zone, biome, usv) %>%
  filter(n() > 100) %>% 
  do(sample_n(., 350)) %>%
  ungroup
```

### Perform for Abejas with stratified sampling

```{r}
# Get DF
abejas_df <- div_df %>% filter(pol_group == 'Abejas')
df_samp <- abejas_df %>%
  group_by(anp_zone, biome, usv) %>% 
  do(sample_n(., 64)) %>% 
  ungroup

# Run for one group
# Get group differences and plot for one group
biomes <- levels(df_samp$biome)
zones <- levels(df_samp$anp_zone)
df_samp1 <- df_samp %>%
  filter(biome == biomes[[6]] & anp_zone == zones[[1]])

# Run
sum1 <- get_grp_differences(df_samp1)

# Plot
ggplot(sum1, aes(x = usv, y = Median, color=Letter)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 4) +
   ylab("Median richness with 95% CI")

# Get group differences for each combination of biome and ANP zone
df_nest <- df_samp %>% group_by(biome, anp_zone) %>% nest()
sum2 <- df_nest %>%
  mutate(sum = purrr::map(data, get_grp_differences_wilcox)) %>%
  select(-data) %>% 
  unnest(cols=sum)

# Plot
ggplot(sum2, aes(x = usv, y = Median, color=Letter)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 2) +
   ylab("Median richness with 95% CI") +
  facet_grid(vars(biome), vars(anp_zone)) +
  labs(caption = "Different colors within one facet indicate statistically significant difference between groups.")
```

### Get group differences (comparing by land cover)

```{r}
# Stratified random sample
# Sample the same cells for all the pollinator groups
samp_n <- 350

samp_idx <- div_df %>% 
  filter(pol_group == 'Abejas') %>% 
  group_by(anp_zone, biome, usv) %>%
  filter(n() >= samp_n) %>% 
  do(sample_n(., samp_n)) %>%
  ungroup

df_samp <- div_df %>% filter(cell %in% samp_idx$cell)

# Get group differences for each combination of biome and ANP zone
df_nest <- df_samp %>% group_by(pol_group, biome, anp_zone) %>% nest()
sum2 <- df_nest %>%
  mutate(sum = purrr::map(data, get_grp_differences_wilcox)) %>%
  select(-data) %>% 
  unnest(cols=sum)

# Save 
fn <- str_c('grpdiffs_samp', samp_n, '_USV_', params$rich_code, '_', 
            datefilt_code, '_', params$nspecies, 'species_',
            length(levels(sum2$pol_group)), 'pols.csv')
grp_diffs_fp <- file.path(div_dir, fn)
sum2 %>% write_csv(grp_diffs_fp)
```

## Perform by pollinator group
### Define plotting function to create facets biome x ANP zone with groups by USV

```{r}
plot_pollin_facet <- function(df, pol_group,
                              patch.position='inner', legend_on=FALSE){
  
  xmax <- max(df$Percentile.upper)
  
  p <- ggplot(df, aes(y = usv, x = Median, color=Letter)) +
  
    # shade facet by ANP zone
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf,
                  fill=anp_zone), alpha=0.2, color='white') +
    scale_fill_grey(name='ANP zone', start=0.1, end=0.9) +
  
    # plot CIs
    geom_errorbar(aes(y = usv, x = Median, color=Letter,
                      xmin = Percentile.lower, xmax = Percentile.upper),
                   width = 0.1, size  = 0.5) +
    
    # plot medians
     geom_point(aes(y = usv, x = Median, color=Letter), 
                shape = 15, size  = 2) +
     xlab("Median richness with 95% CI") +
    
    scale_color_manual(values=c('a'='salmon', 'ab'='#C77CFF', 'b'='#00BFC4', 
                       'bc'='green', 'c'='goldenrod'), 
                       name='Group',
                       drop=FALSE) +
      
    scale_y_discrete(limits = c( 'otro', 'ag', 'veg')) +
    scale_x_continuous(
      breaks=scales::pretty_breaks(4),
                       # breaks=scales::breaks_extended(4),
                       # n.breaks=4,
      limits = c(0, ceiling(xmax)+.2)
      ) +
  
    # Facet by x=pollinator group, y = ANP zone
    facet_grid(vars(anp_zone), vars(biome)) +
    ggtitle(pol_group) +
    theme_minimal() +
    theme(axis.title = element_blank(), 
      plot.title = element_text(size=rel(1), face='bold', hjust=0),
      panel.spacing = unit(0.5, 'mm'),
      panel.border=element_blank(),
      panel.grid.major.y=element_blank(),
      panel.grid.minor.x=element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.x = element_text(margin = margin(t = .2, unit = "mm")),
      strip.text.y = element_blank(),
      strip.background = element_blank(),
      strip.switch.pad.grid = unit(0.5, 'mm')
      )
  
  if(patch.position != 'top'){
    p <- p +
      theme(
        strip.text.x = element_blank()
      )
  }
  
  if(!legend_on){
    p <- p + theme(
      legend.position = 'none'
    )
  }
  
  return(p)
  
}
```

### Plot by biome x ANP zone

```{r}
# Plot
pol_groups <- levels(sum2$pol_group)
(p1 <- sum2 %>% filter(pol_group == pol_groups[1]) %>% 
  plot_pollin_facet(pol_groups[1], patch.position='top'))
(p2 <- sum2 %>% filter(pol_group == pol_groups[2]) %>% 
  plot_pollin_facet(pol_groups[2]))
(p3 <- sum2 %>% filter(pol_group == pol_groups[3]) %>% 
  plot_pollin_facet(pol_groups[3]))
(p4 <- sum2 %>% filter(pol_group == pol_groups[4]) %>% 
  plot_pollin_facet(pol_groups[4], legend_on=T))

wrap_plots(p1, p2, p3, p4, ncol=1)+
  plot_layout(guides = 'collect') +
  plot_annotation(caption = "Different colors within one facet indicate statistically significant difference between groups.")
```

### Plot facets by Pollinator x ANP zone

```{r}
# # Plot
# ggplot(sum2, aes(x = usv, y = Median, color=Letter)) +
#    geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
#                  width = 0.05, size  = 0.5) +
#    geom_point(shape = 15, size  = 2) +
#    ylab("Median richness with 95% CI") +
#   facet_grid(vars(pol_group), vars(biome, anp_zone)) +
#   labs(caption = "Different colors within one facet indicate statistically significant difference between groups.")
# 
# # Plot
# ggplot(sum2, aes(x = usv, y = Median, color=Letter)) +
#     coord_flip() +
#   # shade facet by ANP zone
#   geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, 
#                 fill=anp_zone), alpha=0.3, color='white') + 
#   scale_fill_manual(values = c("black", 'gray', "white")) +
# 
#   # plot CIs and medians
#   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
#                  width = 0.05, size  = 0.5) +
#    geom_point(shape = 15, size  = 2) +
#    ylab("Median richness with 95% CI") +
#   
#   # Facet by x=pollinator group, y = biome and ANP zone
#   facet_grid(vars(biome, anp_zone), vars(pol_group)) +
#   theme(strip.text.y.right = element_text(angle = 0)) +
#   labs(caption = "Different colors within one facet indicate statistically significant difference between groups.")

plot_biome_facet <- function(df, biome_name){
  ggplot(df, aes(y = usv, x = Median, color=Letter)) +
  
    # shade facet by ANP zone
    geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf,
                  fill=anp_zone), alpha=0.2, color='white') +
    # scale_fill_manual(values = c("darkgray", 'lightgray', "white"), name='ANP zone') +
    scale_fill_grey(name='ANP zone', start=0.1, end=0.9) +
  
    # plot CIs
    geom_errorbar(aes(y = usv, x = Median, color=Letter,
                      xmin = Percentile.lower, xmax = Percentile.upper),
                   width = 0.1, size  = 0.5) +
    
    # plot medians
     geom_point(aes(y = usv, x = Median, color=Letter), 
                shape = 15, size  = 2) +
     xlab("Median richness with 95% CI") +
    
    scale_color_manual(values=c('a'='salmon', 'ab'='#C77CFF', 'b'='#00BFC4', 
                       'bc'='green', 'c'='goldenrod'), 
                       name='Group',
                       drop=FALSE) +
  
    # Facet by x=pollinator group, y = ANP zone
    facet_grid(vars(anp_zone), vars(pol_group)) +
    theme(strip.text.y = element_blank()) +
    ggtitle(biome_name)
}

# Plot
biomes <- levels(sum2$biome)
(p1 <- sum2 %>% filter(biome == biomes[1]) %>% 
  plot_biome_facet(biomes[1]))
p2 <- sum2 %>% filter(biome == biomes[2]) %>% 
  plot_biome_facet(biomes[2])
p3 <- sum2 %>% filter(biome == biomes[3]) %>% 
  plot_biome_facet(biomes[3])
p4 <- sum2 %>% filter(biome == biomes[4]) %>% 
  plot_biome_facet(biomes[4])
p5 <- sum2 %>% filter(biome == biomes[5]) %>% 
  plot_biome_facet(biomes[5])
p6 <- sum2 %>% filter(biome == biomes[6]) %>% 
  plot_biome_facet(biomes[6])
p7 <- sum2 %>% filter(biome == biomes[7]) %>% 
  plot_biome_facet(biomes[7])

wrap_plots(p1, p2, p3, p4, p5, p6, p7)+
  plot_layout(guides = 'collect') +
  plot_annotation(caption = "Different colors within one facet indicate statistically significant difference between groups.") &
  scale_x_continuous(limits = c(0, 5)) &
  scale_y_discrete(limits = c( 'otro', 'ag', 'veg')) &
  # theme_classic() &
  theme(axis.title = element_blank(), 
        # strip.text = element_blank(),
        plot.title = element_text(size=10)
        # axis.ticks = element_blank(), 
        # axis.text = element_blank()
        )
```

```{r}
# Get DF
div_df %>%
  pivot_wider()
sub_idx <- div_df %>%
  pivot_wider()
  rownames_to_column() %>% 
  group_by(anp_zone, biome, usv) %>% 
  do(sample_n(., 64)) %>% 
  ungroup %>% 
  select(rownames)
df_samp <- div_df %>%
  group_by(pol_group, anp_zone, biome, usv) %>% 
  do(sample_n(., 64)) %>% 
  ungroup

# Get group differences and plot for one group
biomes <- df_samp %>% distinct(biome) %>% deframe
zones <- df_samp %>% distinct(anp_zone) %>% deframe
df_samp1 <- df_samp %>% 
  filter(biome == biomes[[3]] & anp_zone == zones[[1]])
sum1 <- get_grp_differences(df_samp1)

# Plot
ggplot(sum1, aes(x = usv, y = Median, color=Letter)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 4) +
   ylab("Median richness with 95% CI")

# Get group differences for each combination of biome and ANP zone
df_nest <- df_samp %>% group_by(biome, anp_zone) %>% nest()
sum2 <- df_nest %>%
  mutate(sum = purrr::map(data, get_grp_differences)) %>%
  select(-data) %>% 
  unnest(cols=sum)

# Plot
ggplot(sum2, aes(x = usv, y = Median, color=Letter)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 2) +
   ylab("Median richness with 95% CI") +
  facet_grid(vars(biome), vars(anp_zone)) +
  labs(caption = "Different colors within one facet indicate statistically significant difference between groups.")
```

### Colibries

```{r compare colibries, echo=TRUE}
clbri_df <- div_df %>% filter(pol_group == 'Colibries')
clbri_df <- div_df %>% 
  mutate(anp_zone = as.factor(anp_zone))
m <- lm(richness ~ anp_zone, data = clbri_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(anp_zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
```

### Mariposas

```{r compare mariposas, echo=TRUE}
mrpsa_df <- div_df %>% filter(pol_group == 'Mariposas', stat=='median')
m <- lm(richness ~ zone, data = mrpsa_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
```

## Other methods, in progress

```{r, eval=FALSE}
# Compute mean AGB for each LC (zonal statistics) 
zonal_stats <- terra::zonal(rich_ras, polys_ras, 'mean', na.rm=T)
ex <- terra::extract(rich_ras, polys)
```

