---
title: "explore_richness_stats"
output: html_document
output_file: "test.html"
date: 2021-03-22
editor_options: 
  chunk_output_type: console
params:
  unq_cells: TRUE
  mutually_exclusive_pa: TRUE
  filt_dates: TRUE
  nspecies: 15
  buffer_distance: 10
  rich_code: 'Likhd'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Load libraries and initialize variables

#### Parameters

rich_code: `params$rich_code`
unq_cells: `params$unq_cells`
mutually_exclusive_pa: `params$mutually_exclusive_pa`
filt_dates: `params$filt_dates`
nspecies: `params$nspecies`
buffer_distance: `params$buffer_distance` km

```{r initialize, message=FALSE}
library(tidyverse)

# Parameters
rich_code <- params$rich_code

sessionInfo()
```

## Extract zonal stats

```{r, collapse=TRUE, eval=TRUE}
# directory paths
unq_code <- ifelse(params$mutually_exclusive_pa, 'unq_cells_exclusive', unq_code)
datefilt_code <- ifelse(params$filt_dates, '2000to2020', 'alldates')
bind_fn <- str_c('ANPs_allzones_buff', params$buffer_distance,'km')
bind_fp <- here::here('data', 'data_out', 'ANPs', str_c(bind_fn, '.gpkg'))

for(pol_group in c('Abejas', 'Colibries', 'Mariposas')){
  # directory paths
  fp_tail <- file.path('sdm', str_c(unq_code, '_', datefilt_code), 'rf1', pol_group)
  pred_dir <- here::here('data', 'data_out', fp_tail)
  
  # File paths
  fn <- str_glue('{rich_code}_rich_{pol_group}_{datefilt_code}_{params$nspecies}species')
  rich_tif_fp <- here::here(pred_dir, str_glue('{fn}.tif'))
  div_dir <- here::here('data', 'data_out', 'diversity_by_zones', 
                          'from_richness', bind_fn)
  div_df_fp <- file.path(div_dir, str_c(fn, '.csv'))

  if(!file.exists(div_df_fp)){
    # Load raster
    rich_ras <- raster::raster(rich_tif_fp)
    
    # Load polygons
    polys <- sf::st_read(bind_fp) 
    polys_sp <- sf::as_Spatial(polys)
    
    # Zonal statistics
    zon <- spatialEco::zonal.stats(polys_sp, rich_ras, stats=c('mean', 'median'))
    names(zon) <- c('mean', 'median')
    
    div_df <- tibble(polys_sp@data) %>% 
      bind_cols(zon) %>% 
      mutate(zone = as.factor(zone),
             pol_group = pol_group) %>% 
      pivot_longer(cols=any_of(c('mean', 'median')), names_to='stat', values_to='richness')
    
    # Save DF
    dir.create(dirname(div_df_fp), recursive=T, showWarnings = F)
    div_df %>% write_csv(div_df_fp)
  }
}

# Load DFs and row bind
(fps <- list.files(div_dir, pattern='csv$', full.name=T) %>% 
    str_subset(str_glue('{rich_code}.*{datefilt_code}')))
div_df <- fps %>% purrr::map_dfr(read_csv, col_types='ccdfffd') 
```

## Plots
### Histograms

```{r histograms, echo=TRUE, collapse=TRUE}
div_df %>%
  filter(stat == 'median') %>% 
  ggplot(., aes(x=richness, fill=zone)) +
  geom_histogram() +
  theme(legend.position = 'none') +
  facet_grid(rows=vars(zone), cols=vars(pol_group), scales = 'free_x')
```

### Boxplots

```{r boxplots, echo=TRUE, collapse=TRUE}
div_df %>% 
  filter(stat == 'median') %>% 
  ggplot(., aes(x=richness, fill=zone, y=zone)) +
  geom_boxplot() +
  theme(legend.position = 'none')  +
  labs(y=NULL) +
  facet_wrap(facets=vars(pol_group), nrow=3, scales = 'free_x')
```

## Check for significant differences in groups
### Abejas

```{r compare abejas, echo=TRUE}
abejas_df <- div_df %>% filter(pol_group == 'Abejas', stat=='median')
m <- lm(richness ~ zone, data = abejas_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
# 
# abejas_df %>% 
#   ggplot(., aes(x=richness, fill=zone, y=zone)) +
#   geom_boxplot() +
#   theme(legend.position = 'none')  +
#   labs(y=NULL) 
```

### Colibries

```{r compare colibries, echo=TRUE}
clbri_df <- div_df %>% filter(pol_group == 'Colibries', stat=='median')
m <- lm(richness ~ zone, data = clbri_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
```

### Mariposas

```{r compare mariposas, echo=TRUE}
mrpsa_df <- div_df %>% filter(pol_group == 'Mariposas', stat=='median')
m <- lm(richness ~ zone, data = mrpsa_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
```

## Other methods, in progress

```{r testing, eval=FALSE}
# Zonal statistics using raster::extract
ex <- raster::extract(rich_ras, polys, fun=median, na.rm=TRUE, df=TRUE)

# Compute mean AGB for each LC (zonal statistics) 
rich_ras <- terra::rast(rich_tif_fp)
polys_ras <- polys %>% to_raster()
zonal_stats <- terra::zonal(rich_ras, polys, 'median', na.rm=T)
```

